Application-Level Regression Testing Framework using Jenkins

### 2017-03-02 manuscript/manuscript.tex
cleaned up typo

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Author1, Timothy Bouvet, Galen Arnold}
%xxxx\IEEEauthorrefmark{3} and
%xxxx\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
National Institute for Computational Sciences\\
The University of Tennessee, Knoxville, TN 37996\\
\{email1,tbouvet@illinois.edu,email3\}@domain.edu}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
%}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{example}
\caption{This is an example figure with its caption.}
\label{fig:example}
\end{figure}

@@

@@

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Author1, Timothy Bouvet, Galen Arnold}
%xxxx\IEEEauthorrefmark{3} and
%xxxx\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
National Institute for Computational Sciences\\
The University of Tennessee, Knoxville, TN 37996\\
\{email1,tbouvet@illinois.edu,gwarnold@illinois.edu\}@domain.edu}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
%}

@@

@@

\begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
#!/bin/bash
echo "=== RUNNING $0 ==="
if [ $# -lt 1 ]
then
  echo "$0: missing argument for jobid"
  exit 1
fi
while true
do
	MYQSTAT=`qstat $1`
	if test "$MYQSTAT" = ""
        then
		echo $1 finished
		exit
	else
		DATE=`date`
		echo "$DATE: waiting for $1 to finish"
	fi
	sleep 5m
done
\end{lstlisting}

@@

\subsection{special projects}
The tabs display of our Jenkins instance is used to group tests and we add tabs for special projects.   For example we clone existing tests for evaluating a new software stack on our test login node.   Our test rack has a separate set of tests from our production system and is used as our Jenkins test development area.  The sustained petascale performance benchmarks are in their own tab since they can run at scale and are only run on-demand (not scheduled by Jenkins ).
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{tabs-display}
\caption{ tabs for project areas }
\label{fig:tabs-display}
\end{figure}
